Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with the Uniform Kernel

### 2016-05-11 main_paper.tex
Tweak reference to git info command
Correct error in inequality in main bootstrap proof
Typo on last part of proof of theorem 2, add square root  when bounding the Mallow's Distance.
Minor typos on the appendix.
Add two lines to the table
The naive estimator and naive bootstrap estimator are added. However, it
seems very difficult to read.

% Add commit information from Git to the pdf. It is automatically
% generated with the R script 'R/version.R' and can be run from
% the command line in the project's top directory via:
%
% $ Rscript R/version.R
%
% If VERSION.tex does not exist we can't add information from
% Git, so we'll use today's date as a fallback.

@@

\begin{algorithm}[Bias estimation]\label{Alg1}
  Assume $h$ and $b$ are bandwidths as defined by Assumption~\ref{A2} and define
  \begin{align*}
    I_{-}(h) &= \{i : -h < X_{i} < 0\}, &
    I_{+}(h) &= \{i : 0 \leq X_{i} < h\}.
  \end{align*}
  Also define $M_{-}(h)$ and $M_{+}(h)$ to be the number of elements in $I_{-}(h)$ and
  $I_{+}(h)$ respectively, and $m_{-}(h,1),\dots,m_{-}(h,M_{-}(h))$ and
  $m_{+}(h,1),\dots,m_{+}(h,M_+(h))$ to be subsequences of $1,\dots,n$ that index
  $I_{-}(h)$ and $I_{+}(h)$, respectively.
  \begin{enumerate}
  \item Estimate local second order polynomials $\hat g_{-}$ and $\hat g_{+}$ using
    the observations in $I_{-}(b)$ and $I_{+}(b)$:
    \begin{align}
      \label{eq:2}
      \hat g_{-}(x)
      &= \hat\beta_{-,0} + \hat\beta_{-,1} x + \hat\beta_{-,2} x^{2},
      &\hat g_{+}(x)
      &= \hat\beta_{+,0} + \hat\beta_{+,1} x + \hat\beta_{+,2} x^{2}
    \end{align}
    with
    \begin{align*}
      \hat\beta_{-} &= \argmin_\beta \sum_{i \in I_-(b)}
      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^2 \\
      \hat\beta_{+} &= \argmin_\beta \sum_{i \in I_+(b)}
      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^2.
    \end{align*}
    Calculate the residuals
    \begin{equation}
      \label{eq:3}
      \hat\varepsilon_{i} =
      \begin{cases}
        Y_{i} - \hat g_-(X_{i}) & \textif\ X_{i} < 0 \\
        Y_{i} - \hat g_+(X_{i}) & \otherwise.
      \end{cases}
    \end{equation}
  \item Repeat the following steps $B_{1}$ times to produce the
    bootstrap estimates $\hat{\tau}_{1}^{*}(h),\dots,\hat\tau_{B_{1}}^{*}(h)$. For the
    $k$th value:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M_-(b)$ from
      $\{\hat\varepsilon_i : i \in I_-(b)\}$ and one of size $M_+(b)$ from
      $\{\hat\varepsilon_i : i \in I_+(b)\}$. Let $\varepsilon_{-,i}^{*}$ and
      $\varepsilon_{+,i}^{*}$ denote the $i$th element of each sample and
      construct
      \begin{align*}
        Y_{-,m_-(h,i)}^* &= \hat g_-(X_{m_-(h,i)}) + \varepsilon_{-,i}^{*} &
        Y_{+,m_+(h,i)}^* &= \hat g_+(X_{m_-(h,i)}) + \varepsilon_{+,i}^{*}.
      \end{align*}
    \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
      local linear model on the bootstrap data set:\footnote{%
        Note that the indices of summation are chosen to correspond to the
        indices of the variables generated in the previous step.} %
      \begin{align*}
        \hat\mu_-^*(h)
        &= \argmin_{\mu} \min_{\beta} \ssum[-]{i}{h}
          (Y_i^* - \mu - \beta X_i^*)^2 \\
        \hat\mu_+^*(h)
        &= \argmin_{\mu} \min_{\beta} \ssum[+]{i}{h}
          (Y_i^* - \mu - \beta X_i^*)^2.
      \end{align*}
    \item Save $\hat\tau^*_k(h) = \hat\mu_+^*(h) - \hat\mu_-^*(h)$.
    \end{enumerate}
  \item Estimate the bias as
    \begin{equation}
      \label{eq:9}
      \Delta^*(h,b) = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k(h) -
      \big[\hat g_+(0) - \hat g_-(0)\big].
    \end{equation}
  \end{enumerate}
\end{algorithm}
Note that $\hat g_+(0) - \hat g_-(0)$ is the true treatment effect under the
distribution induced by this bootstrap. The bootstrap estimator works by
constructing an approximate DGP with known properties. As the dataset gets
larger, the approximate DGP mimics the unknown real DGP more closely, and the
population parameter values in the bootstrap DGP can become accurate estimates
of the true parameter values in the real DGP.

@@

\begin{algorithm}[Confidence intervals]\label{Alg2}
  Define the same notation as in Algorithm~\ref{Alg1}.
  \begin{enumerate}
  \item Estimate $\hat g_+$ and $g_-$ and generate the residuals
    $\hat\varepsilon_i$ just as in Algorithm~\ref{Alg1}.
  \item Repeat the following steps $B_{2}$ times to produce the
    bootstrap estimates
    $\hat\tau_1^{\prime*}(h,b), \dots, \hat\tau_{B_{2}}^{\prime*}(h,b)$. For the
    $k$th value:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M_-(b)$ from
      $\{\hat\varepsilon_i : i \in I_-(b)\}$ and one of size $M_+(b)$ from
      $\{\hat\varepsilon_i : i \in I_+(b)\}$. Let $\varepsilon_{-,i}^{*}$ and
      $\varepsilon_{+,i}^{*}$ denote the $i$th element of each sample and
      construct
      \begin{align*}
        Y_{-,m_-(h,i)}^* &= \hat g_-(X_{m_-(h,i)}) + \varepsilon_{-,i}^{*} &
        Y_{+,m_+(h,i)}^* &= \hat g_+(X_{m_{+}(h,i)}) + \varepsilon_{+,i}^{*}.
      \end{align*}
    \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
      local linear model on the bootstrap data set:
      \begin{align*}
        \hat\mu_-^*(h)
        &= \argmin_{\mu} \min_{\beta} \ssum[-]{i}{h}
          (Y_i^* - \mu - \beta X_i^*)^2 \\
        \hat\mu_+^*(h)
        &= \argmin_{\mu} \min_{\beta} \ssum[+]{i}{h}
          (Y_i^* - \mu - \beta X_i^*)^2.
      \end{align*}
    \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set,
      \begin{multline*}
        (Y_{-,m_-(b,1)}^{*}, X_{-,m_-(b,1)}),\dots,
        (Y_{-,m_-(b,M_-(b))}^{*},X_{-,m_-(b,M_-(b))}), \\
        (Y_{+,m_+(b,1)}^{*}, X_{+,m_+(b,1)}),\dots,
        (Y_{+,m_+(b,M_+(b))}^{*},X_{+,m_+(b,M_+(b))})
      \end{multline*}
      using the same bandwidths $h$ and $b$ that are used in the rest of this
      algorithm but reestimating all of the local polynomials on the bootstrap
      data. Generate $B_1$ new bootstrap samples and let $\Delta^{**}(h,b)$
      represent the bias estimator returned by Algorithm~\ref{Alg1}.
    \item Save the bias-corrected estimator
      $\hat\tau_k^{\prime*}(h,b) = \hat\mu_+^*(h) - \hat\mu_i^*(h)
      - \Delta^{**}(h,b)$.
    \end{enumerate}
  \item Use the empirical CDF of
    $\hat\tau_1^{\prime*}(h,b),\dots \hat\tau_{B_2}^{\prime*}(h,b)$ to
    construct confidence intervals, etc.
  \end{enumerate}
\end{algorithm}

@@

We also show the coverage of two of CCT's interval estimators for comparison.
We estimate their bias corrected procedure with AMSE-optimal bandwidths for both
the uniform kernel and the triangular kernel. The uniform kernel provides a
direct comparison with our bootstrap, while the triangular kernel may be more
appealing to practitioners. Since CCT establish conclusively that the ``naive''
uncorrected interval estimator has poor coverage in these settings we do not
report results for that estimator.

\begin{table}[t]
  \centering
  \begin{tabular}{rlrrrrrrr}
    \toprule
    DGP & Method     & Bias   & SD    & RMSE   & CI Coverage (\%) & CI Length \\
    \midrule
    1   & \bootuni   & --0.014 & 0.067 & 0.069 & 93.4       & 0.242     \\
        & \cctuni    & --0.014 & 0.067 & 0.069 & 92.5       & 0.246     \\
        & \ccttri    & --0.014 & 0.067 & 0.068 & 91.4       & 0.239     \\\\
    2   & \bootuni   & --0.011 & 0.088 & 0.089 & 95.1       & 0.323     \\
        & \cctuni    & --0.011 & 0.088 & 0.089 & 93.7       & 0.353     \\
        & \ccttri    & --0.008 & 0.086 & 0.086 & 93.2       & 0.346     \\\\
    3   & \bootuni   & --0.004 & 0.065 & 0.065 & 95.9       & 0.247     \\
        & \cctuni    & --0.004 & 0.065 & 0.065 & 93.8       & 0.251     \\
        & \ccttri    & --0.005 & 0.065 & 0.065 & 93.4       & 0.244     \\
    \bottomrule
  \end{tabular}
  \caption{%
    Experimental coverage probabilities for each interval estimator based on 5000
    simulations; nominal coverage probabilities are 95\% for each estimator. The column
    ``CI Coverage'' lists the coverage frequency in these simulations and ``CI Length''
    lists the average length of the confidence interval across simulations.}
  \label{tbl:1}
\end{table}

Table~\ref{tbl:1} presents the results of these simulations. The rows labeled
``\bootuni'' show results for our proposed bootstrap interval; ``\cctuni'' and
``\ccttri'' show results for the analytically-corrected intervals. The first
three columns give the bias, standard deviation, and Root-MSE of the \emph{bias corrected} point
estimators corresponding to each confidence interval.  As expected, these
estimators are close to unbiased, with their standard deviation largely
determining the estimators' RMSE. Moreover, as Theorem~\ref{T1} suggests, the
bootstrap and analytically-corrected estimators have essentially the same
standard deviation across all of the DGPs.

The column ``CI Coverage'' lists the experimental coverage of each interval.
All of the intervals are reasonably close to their nominal coverage, although
the analytically corrected estimators seem to persistently under-cover the true 
ATE (especially the one using triangular kernel). Our proposed bootstrap
procedure consistently performs well, as it is about a percentage point closer
to nominal coverage than the other interval estimators in DGPs 1 and 2, and is
slightly conservative (95.9\% coverage) in DGP 3. The final column, ``CI Length,''
indicates that all three of these procedures generate intervals that are
approximately the same length on average.

@@

\appendix
\section{Mathematical appendix}
Let $e_p$ be the selection vector with 1 in element $p+1$ and 0
everywhere else. Define the following additional notation:\footnote{%
  As we mention in Section~\ref{background}, we have adopted CCT's
  notation where possible and these terms originate in that paper.} %
$r_p(x) = (1,\ x,\dots,\ x^p)'$,
\begin{align*}
  (\hat{\mu}_{+,p}(h),\ \hat{\mu}_{+,p}^{(1)}(h),\dots,\ \hat\mu_{+,p}^{(p)}(h))'
  &= \argmin_{\beta} \ssum[+]{i}{h} (Y_i - r_p(X_i/h)'\beta)^2 \\
  (\hat{\mu}_{-,p}(h),\ \hat{\mu}_{-,p}^{(1)}(h),\dots,\ \hat\mu_{-,p}^{(p)}(h))'
  &= \argmin_{\beta} \ssum[-]{i}{h} (Y_i - r_p(X_i/h)'\beta)^2
\end{align*}
and
\begin{align*}
  \Gamma_{+,p}(h) &= \tfrac{1}{nh} \ssum[+]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
  \Gamma_{-,p}(h) &= \tfrac{1}{nh} \ssum[-]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
  \Psi_{+,p,q}(h,b)
  &= \tfrac{1}{nhb} \ssum[+]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
    \V(Y_i \mid X_i) \\
  \Psi_{-,p,q}(h,b)
  &= \tfrac{1}{nhb} \ssum[-]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
    \V(Y_i \mid X_i) \\
  \Bf_+(h)
  & = e_0' \Gamma_{+,1}^{-1}
    \ssum[+]{i}{h} r_1(X_i/h) \; X_i^2 / h^2, \\
  \Bf_-(h)
  & = e_0' \Gamma_{-,1}^{-1}
    \ssum[-]{i}{h} r_1(X_i/h) \; X_i^2 / h^2.
\end{align*}

@@

Notice that~\eqref{eq:6} implies that
\begin{equation*}
  \hat\tau(h) - \Delta^*(h,b) - \tau
  =^d \Omega_{+}(h,b)' \epb_{+} - \Omega_{-}(h,b)' \epb_{-} + O_p(h^3),
\end{equation*}
with $\epb_+$ an i.i.d. random vector of length $M_+(b)$, the $i$th
element of which is distributed as
\[
  \varepsilon_{i,+} =^d
  \begin{cases}
    Y_{m_+(1,b)} - \E(Y_{m_+(1,b)} \mid X_{m_+(1,b)})
    & \text{with probability\ } 1/M_+(b) \\
    \vdots \\
    Y_{m_+(M_+(b),b)} - \E(Y_{m_+(M_+(b),b)} \mid X_{m_+(1,b)})
    & \text{with probability\ } 1/M_+(b),
  \end{cases}
\]
and $\epb_-$ the corresponding quantity after replacing ``+'' with
``--.''  Consequently, it suffices to prove that
\begin{gather}
  \label{eq:7}
  \rho(V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}^{*},\
    V'(h,b)^{-1/2}\Omega_+(h,b)'\epb_{+}) \to^p 0
  \intertext{and}
  \label{eq:8}
  \rho(V'(h,b)^{-1/2}\Omega_-(b)'\epb_{-}^{*},\
    V'(h,b)^{-1/2}\Omega_-(b)'\epb_{-}) \to^p 0
\end{gather}
with $\rho$ the ``Mallows metric'' used by
\citet{bickel1981}.\footnote{%
  For two random vectors $u$ and $v$ with finite 2nd moments,
  $\rho(u, v)$ is defined as
  \begin{equation*}
    \rho(u, v) = \inf\nolimits_{(U, V)\ s.t.\ U =^d u,\ V =^d v}
    \big(\E \lVert U - V \rVert^2\big)^{1/2}.
  \end{equation*}}
Convergence in $\rho$ is equivalent to convergence in both distribution
and second moments. \citep[Lemma 8.3.]{bickel1981}

We will only prove~\eqref{eq:7} since the proof of~\eqref{eq:8} is
identical. By Theorem 2.1 of \cite{freedman1981}, we have
\begin{align*}
  \rho(V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}^{*},\
  &V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}) \\
  &\leq \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times
    \tr(V'(h,b)^{-1/2} \Omega_+(h,b)' \Omega_+(h,b)V'(h,b)^{-1/2}) \\
  &= \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times O_{p^{*}}(1),
\end{align*}
the second line holding as a consequence of CCT's Lemma SA1. So it suffices
to show that $\rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \to^{p^{*}} 0$. Let
$\varepsilon^\circ_i$ be an i.i.d. sequence randomly drawn from the
realized values of $\epb_+$ with replacement and let
$\bar{\varepsilon}^\circ = (1/M_+(b)) \osum[+]{i}{b} \varepsilon^\circ_i$. Then,
using the same arguments as \cite{freedman1981}, we have the upper bound
\begin{equation*}
  \rho(\varepsilon_{+,1}^*, \varepsilon_{+,1})
  \leq
  (\bar\varepsilon^{\circ})^2 +
  (2/M_+(b)) \osum[+]{i}{b} (\hat\varepsilon_i - \varepsilon_i)^2
  + \rho(\varepsilon^\circ_1,\ \varepsilon_{+,1}).
\end{equation*}
But $(\bar\varepsilon^{\circ})^2 \to^p 0$ by the LLN,
\[
  (1/M_+(b)) \osum[+]{i}{b}
  \E((\hat\varepsilon_i - \varepsilon_i)^2 \mid X_i) \to 0
\]
by CCT's Lemma SA1, and
$\rho(\varepsilon_1^\circ,\ \varepsilon_{+,1}) \to^p 0$ by Lemma~8.4 of
\cite{bickel1981}.\qed

>>>>

% Add commit information from Git to the pdf. It is automatically
% generated with the R script 'tex/git and can be run from
% the command line in the project's top directory via:
%
% $ tex/git
%
% If VERSION.tex does not exist we can't add information from
% Git, so we'll use today's date as a fallback.

@@

\begin{algorithm}[Bias estimation]\label{Alg1}
  Assume $h$ and $b$ are bandwidths as defined by Assumption~\ref{A2} and define
  \begin{align*}
    I_{-}(h) &= \{i : -h < X_{i} < 0\}, &
    I_{+}(h) &= \{i : 0 \leq X_{i} < h\}.
  \end{align*}
  Also define $M_{-}(h)$ and $M_{+}(h)$ to be the number of elements in $I_{-}(h)$ and
  $I_{+}(h)$ respectively, and $m_{-}(h,1),\dots,m_{-}(h,M_{-}(h))$ and
  $m_{+}(h,1),\dots,m_{+}(h,M_+(h))$ to be subsequences of $1,\dots,n$ that index
  $I_{-}(h)$ and $I_{+}(h)$, respectively.
  \begin{enumerate}
  \item Estimate local second order polynomials $\hat g_{-}$ and $\hat g_{+}$ using
    the observations in $I_{-}(b)$ and $I_{+}(b)$:
    \begin{align}
      \label{eq:2}
      \hat g_{-}(x)
      &= \hat\beta_{-,0} + \hat\beta_{-,1} x + \hat\beta_{-,2} x^{2},
      &\hat g_{+}(x)
      &= \hat\beta_{+,0} + \hat\beta_{+,1} x + \hat\beta_{+,2} x^{2}
    \end{align}
    with
    \begin{align*}
      \hat\beta_{-} &= \argmin_\beta \sum_{i \in I_-(b)}
      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^2 \\
      \hat\beta_{+} &= \argmin_\beta \sum_{i \in I_+(b)}
      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^2.
    \end{align*}
    Calculate the residuals
    \begin{equation}
      \label{eq:3}
      \hat\varepsilon_{i} =
      \begin{cases}
        Y_{i} - \hat g_-(X_{i}) & \textif\ X_{i} < 0 \\
        Y_{i} - \hat g_+(X_{i}) & \otherwise.
      \end{cases}
    \end{equation}
  \item Repeat the following steps $B_{1}$ times to produce the
    bootstrap estimates $\hat{\tau}_{1}^{*}(h),\dots,\hat\tau_{B_{1}}^{*}(h)$. For the
    $k$th value:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M_-(b)$ from
      $\{\hat\varepsilon_i : i \in I_-(b)\}$ and one of size $M_+(b)$ from
      $\{\hat\varepsilon_i : i \in I_+(b)\}$. Let $\varepsilon_{-,i}^{*}$ and
      $\varepsilon_{+,i}^{*}$ denote the $i$th element of each sample and
      construct
      \begin{align*}
        Y_{-,m_-(b,i)}^* &= \hat g_-(X_{m_-(b,i)}) + \varepsilon_{-,i}^{*} &
        Y_{+,m_+(b,i)}^* &= \hat g_+(X_{m_-(b,i)}) + \varepsilon_{+,i}^{*}.
      \end{align*}
    \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
      local linear model on the bootstrap data set:\footnote{%
        Note that the indices of summation are chosen to correspond to the
        indices of the variables generated in the previous step.} %
      \begin{align*}
        \hat\mu_-^*(h)
        &= \argmin_{\mu} \min_{\beta} \ssum[-]{i}{h}
          (Y_i^* - \mu - \beta X_i^*)^2 \\
        \hat\mu_+^*(h)
        &= \argmin_{\mu} \min_{\beta} \ssum[+]{i}{h}
          (Y_i^* - \mu - \beta X_i^*)^2.
      \end{align*}
    \item Save $\hat\tau^*_k(h) = \hat\mu_+^*(h) - \hat\mu_-^*(h)$.
    \end{enumerate}
  \item Estimate the bias as
    \begin{equation}
      \label{eq:9}
      \Delta^*(h,b) = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k(h) -
      \big[\hat g_+(0) - \hat g_-(0)\big].
    \end{equation}
  \end{enumerate}
\end{algorithm}
Note that $\hat g_+(0) - \hat g_-(0)$ is the true treatment effect under the
distribution induced by this bootstrap. The bootstrap estimator works by
constructing an approximate DGP with known properties. As the dataset gets
larger, the approximate DGP mimics the unknown real DGP more closely, and the
population parameter values in the bootstrap DGP can become accurate estimates
of the true parameter values in the real DGP.

@@

\begin{algorithm}[Confidence intervals]\label{Alg2}
  Define the same notation as in Algorithm~\ref{Alg1}.
  \begin{enumerate}
  \item Estimate $\hat g_+$ and $g_-$ and generate the residuals
    $\hat\varepsilon_i$ just as in Algorithm~\ref{Alg1}.
  \item Repeat the following steps $B_{2}$ times to produce the
    bootstrap estimates
    $\hat\tau_1^{\prime*}(h,b), \dots, \hat\tau_{B_{2}}^{\prime*}(h,b)$. For the
    $k$th value:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M_-(b)$ from
      $\{\hat\varepsilon_i : i \in I_-(b)\}$ and one of size $M_+(b)$ from
      $\{\hat\varepsilon_i : i \in I_+(b)\}$. Let $\varepsilon_{-,i}^{*}$ and
      $\varepsilon_{+,i}^{*}$ denote the $i$th element of each sample and
      construct
      \begin{align*}
        Y_{-,m_-(b,i)}^* &= \hat g_-(X_{m_-(b,i)}) + \varepsilon_{-,i}^{*} &
        Y_{+,m_+(b,i)}^* &= \hat g_+(X_{m_{+}(b,i)}) + \varepsilon_{+,i}^{*}.
      \end{align*}
    \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
      local linear model on the bootstrap data set:
      \begin{align*}
        \hat\mu_-^*(h)
        &= \argmin_{\mu} \min_{\beta} \ssum[-]{i}{h}
          (Y_i^* - \mu - \beta X_i^*)^2 \\
        \hat\mu_+^*(h)
        &= \argmin_{\mu} \min_{\beta} \ssum[+]{i}{h}
          (Y_i^* - \mu - \beta X_i^*)^2.
      \end{align*}
    \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set,
      \begin{multline*}
        (Y_{-,m_-(b,1)}^{*}, X_{-,m_-(b,1)}),\dots,
        (Y_{-,m_-(b,M_-(b))}^{*},X_{-,m_-(b,M_-(b))}), \\
        (Y_{+,m_+(b,1)}^{*}, X_{+,m_+(b,1)}),\dots,
        (Y_{+,m_+(b,M_+(b))}^{*},X_{+,m_+(b,M_+(b))})
      \end{multline*}
      using the same bandwidths $h$ and $b$ that are used in the rest of this
      algorithm but reestimating all of the local polynomials on the bootstrap
      data. Generate $B_1$ new bootstrap samples and let $\Delta^{**}(h,b)$
      represent the bias estimator returned by Algorithm~\ref{Alg1}.
    \item Save the bias-corrected estimator
      $\hat\tau_k^{\prime*}(h,b) = \hat\mu_+^*(h) - \hat\mu_i^*(h)
      - \Delta^{**}(h,b)$.
    \end{enumerate}
  \item Use the empirical CDF of
    $\hat\tau_1^{\prime*}(h,b),\dots \hat\tau_{B_2}^{\prime*}(h,b)$ to
    construct confidence intervals, etc.
  \end{enumerate}
\end{algorithm}

@@

We also show the coverage of two of CCT's interval estimators for comparison.
We estimate their bias corrected procedure with AMSE-optimal bandwidths for both
the uniform kernel and the triangular kernel. The uniform kernel provides a
direct comparison with our bootstrap, while the triangular kernel may be more
appealing to practitioners.

In addition, we present the coverage of the ``naive'' uncorrected interval 
estimator using the uniform kernel and an optimal bandwidth $h$ proposed by 
\cite{IK}, which has been shown by CCT to have poor coverage. As an alternative, 
we show the coverage of the interval estimator obtained by bootstrapping the 
``naive'' uncorrected point estimate. Specifically, we resample the data with 
equal weights, find optimal bandwidth for each bootstrapped sample and calculate 
the uncorrected point estimate. The $0.025$ and $0.975$ quantiles of the bootstrap 
distribution are used as the lower and upper bound of the confidence interval.

\begin{table}[t]
  \centering
  \begin{tabular}{rlrrrrrrr}
    \toprule
    DGP & Method     & Bias   & SD    & RMSE   & CI Coverage (\%) & CI Length \\
    \midrule
    1   & \bootuni   & --0.014 & 0.067 & 0.069 & 93.4       & 0.242     \\
	    & \bootnaive & --0.040 & 0.042 & 0.058 & 89.0       & 0.182     \\
        & \cctuni    & --0.014 & 0.067 & 0.069 & 92.5       & 0.246     \\
        & \ccttri    & --0.011 & 0.067 & 0.068 & 91.4       & 0.239     \\
        & \naiveuni  & --0.040 & 0.042 & 0.058 & 81.5       & 0.156     \\\\
    2   & \bootuni   & --0.011 & 0.088 & 0.089 & 95.3       & 0.323     \\
        & \bootnaive & --0.151 & 0.067 & 0.165 & 35.4       & 0.269     \\
        & \cctuni    & --0.011 & 0.088 & 0.089 & 93.7       & 0.353     \\
        & \ccttri    & --0.008 & 0.086 & 0.086 & 93.2       & 0.346     \\
        & \naiveuni  & --0.151 & 0.067 & 0.165 & 29.5       & 0.230     \\\\
    3   & \bootuni   & --0.004 & 0.065 & 0.065 & 95.9       & 0.247     \\
	    & \bootnaive &   0.033 & 0.052 & 0.062 & 91.3       & 0.215     \\
        & \cctuni    & --0.004 & 0.065 & 0.065 & 93.8       & 0.251     \\
        & \ccttri    & --0.005 & 0.065 & 0.065 & 93.4       & 0.244     \\
        & \naiveuni  &   0.033 & 0.052 & 0.062 & 86.1       & 0.191     \\
    \bottomrule
  \end{tabular}
  \caption{%
    Experimental coverage probabilities for each interval estimator based on 5000
    simulations; nominal coverage probabilities are 95\% for each estimator. The column
    ``CI Coverage'' lists the coverage frequency in these simulations and ``CI Length''
    lists the average length of the confidence interval across simulations.}
  \label{tbl:1}
\end{table}

Table~\ref{tbl:1} presents the results of these simulations. The rows labeled
``\bootuni'' show results for our proposed bootstrap interval; ``\bootnaive'' 
show results for the naive bootstrap interval; ``\cctuni'' and ``\ccttri'' show 
results for the analytically-corrected intervals; and ``\naiveuni'' show results 
for the analytically-uncorrected interval. The first three columns give the bias, 
standard deviation, and Root-MSE of the point
estimators corresponding to each confidence interval.  As expected, the three 
bias corrected estimators (``\bootuni'', ``\cctuni'' and ``\ccttri'') have 
bias close to zero, with their standard deviation largely
determining the estimators' RMSE. Moreover, as Theorem~\ref{T1} suggests, the
bootstrap and analytically-corrected estimators have essentially the same
standard deviation across all of the DGPs.

The column ``CI Coverage'' lists the experimental coverage of each interval.
All of the intervals from three robust estimators are reasonably close to their nominal coverage, although
the analytically corrected estimators seem to persistently under-cover the true 
ATE (especially the one using triangular kernel). Our proposed bootstrap
procedure consistently performs well, as it is about a percentage point closer
to nominal coverage than the other interval estimators in DGPs 1 and 2, and is
slightly conservative (95.9\% coverage) in DGP 3. The final column, ``CI Length,''
indicates that all three of these procedures generate intervals that are
approximately the same length on average.

@@

\appendix
\section{Mathematical appendix}
Let $e_p$ be the selection vector with 1 in element $p+1$ and 0
everywhere else. Define the following additional notation:\footnote{%
  As we mention in Section~\ref{background}, we have adopted CCT's
  notation where possible and these terms originate in that paper.} %
$r_p(x) = (1,\ x,\dots,\ x^p)'$,
\begin{align*}
  (\hat{\mu}_{+,p}(h),\ \hat{\mu}_{+,p}^{(1)}(h),\dots,\ \hat\mu_{+,p}^{(p)}(h))'
  &= \argmin_{\beta} \ssum[+]{i}{h} (Y_i - r_p(X_i/h)'\beta)^2 \\
  (\hat{\mu}_{-,p}(h),\ \hat{\mu}_{-,p}^{(1)}(h),\dots,\ \hat\mu_{-,p}^{(p)}(h))'
  &= \argmin_{\beta} \ssum[-]{i}{h} (Y_i - r_p(X_i/h)'\beta)^2
\end{align*}
and
\begin{align*}
  \Gamma_{+,p}(h) &= \tfrac{1}{nh} \ssum[+]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
  \Gamma_{-,p}(h) &= \tfrac{1}{nh} \ssum[-]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
  \Psi_{+,p,q}(h,b)
  &= \tfrac{1}{nhb} \ssum[+]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
    \V(Y_i \mid X_i) \\
  \Psi_{-,p,q}(h,b)
  &= \tfrac{1}{nhb} \ssum[-]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
    \V(Y_i \mid X_i) \\
  \Bf_+(h)
  & = e_0' \Gamma_{+,1}^{-1}(h)
    \ssum[+]{i}{h} r_1(X_i/h) \; X_i^2 / h^2, \\
  \Bf_-(h)
  & = e_0' \Gamma_{-,1}^{-1}(h)
    \ssum[-]{i}{h} r_1(X_i/h) \; X_i^2 / h^2.
\end{align*}

@@

Notice that~\eqref{eq:6} implies that
\begin{equation*}
  \hat\tau(h) - \Delta^*(h,b) - \tau
  =^d \Omega_{+}(h,b)' \epb_{+} - \Omega_{-}(h,b)' \epb_{-} + O_p(h^3),
\end{equation*}
with $\epb_+$ an i.i.d. random vector of length $M_+(b)$, the $i$th
element of which is distributed as
\[
  \varepsilon_{i,+} =^d
  \begin{cases}
    Y_{m_+(1,b)} - \E(Y_{m_+(1,b)} \mid X_{m_+(1,b)})
    & \text{with probability\ } 1/M_+(b) \\
    \vdots \\
    Y_{m_+(M_+(b),b)} - \E(Y_{m_+(M_+(b),b)} \mid X_{m_+(M_+(b),b)})
    & \text{with probability\ } 1/M_+(b),
  \end{cases}
\]
and $\epb_-$ the corresponding quantity after replacing ``+'' with
``--.''  Consequently, it suffices to prove that
\begin{gather}
  \label{eq:7}
  \rho(V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}^{*},\
    V'(h,b)^{-1/2}\Omega_+(h,b)'\epb_{+}) \to^p 0
  \intertext{and}
  \label{eq:8}
  \rho(V'(h,b)^{-1/2}\Omega_-(b)'\epb_{-}^{*},\
    V'(h,b)^{-1/2}\Omega_-(b)'\epb_{-}) \to^p 0
\end{gather}
with $\rho$ the ``Mallows metric'' used by
\citet{bickel1981}.\footnote{%
  For two random vectors $u$ and $v$ with finite 2nd moments,
  $\rho(u, v)$ is defined as
  \begin{equation*}
    \rho(u, v) = \inf\nolimits_{(U, V)\ s.t.\ U =^d u,\ V =^d v}
    \big(\E \lVert U - V \rVert^2\big)^{1/2}.
  \end{equation*}}
Convergence in $\rho$ is equivalent to convergence in both distribution
and second moments. \citep[Lemma 8.3.]{bickel1981}
